Haploid Selection, Sex Ratio Bias, and Transitions Between sex-determination systems

### 2017-08-10 LaTeX/Turnover.tex
new figure 2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
\includegraphics[width=0.45\linewidth]{regionplot_2a}
\includegraphics[width=0.45\linewidth]{BothWsInvade_Overdominance}
\caption{
In the absence of haploid selection, both neo-W haplotypes can spread in an XY system when there is overdominance.
Panel A shows the range of male homozygote fitnesses that allow both neo-W haplotypes to invade.
Panel B shows the temporal dynamics of the invading neo-W haplotypes; in this case the neo-W does not fix, leading to a polymorphic sex-determining system.
Asterisk in panel A marks parameter values ($w_{aa}^\male=0.15$, $w_{AA}^\male=0.1$) used in panel B.
Parameters: $w_{AA}^\female = w_{aa}^\female = 0.6$, $w_{Aa}^\Hermaphrodite = 1$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$, $r=R=0$.
}
\label{fig:BothOverdominance}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Both neo-W haplotypes can spread, in the absence of haploid selection, when there is overdominance
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\centering
%\includegraphics[width=0.45\linewidth]{regionplot_2a}
\includegraphics[width=0.45\linewidth]{regionplot_2a_Color_Ya_Either}
\includegraphics[width=0.45\linewidth]{BothWsInvade_Overdominance}
\caption{
In the absence of haploid selection, both neo-W haplotypes can spread in an XY system when there is overdominance.
Panel A shows the range of male homozygote fitnesses that allow either neo-W haplotypes to invade.
The blue region overlaps with a red region, where both neo-W haplotypes can invade a population with $A$ fixed on the X and $a$ fixed on the Y.
The green region (overlapped by the orange region) is where both neo-W haplotypes can invade a population with $a$ fixed on the Y and a polymorphic X.
The orange region (outside the green region) is where only the neo-W-$A$ haplotype can invade
Panel B shows the temporal dynamics of the invading neo-W haplotypes; in this case the neo-W does not fix, leading to a polymorphic sex-determining system.
Asterisk in panel A marks parameter values ($w_{aa}^\male=0.15$, $w_{AA}^\male=0.1$) used in panel B.
Parameters: $w_{AA}^\female = w_{aa}^\female = 0.6$, $w_{Aa}^\Hermaphrodite = 1$, $t^\Hermaphrodite = \alpha^\Hermaphrodite_\Delta = 0$, $r=R=0$.
\textcolor{red}{make two more temporal plots with visible asterisks in green and orange regions; figure out better colours to show possibilities}
}
\label{fig:BothOverdominance}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
